---
title: "p8105_hw1_zl3263"
output: github_document
date: "2022-09-23"
---

## Problem 1

**Import library and dataset:**

```{r}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

The variable names are as follow: `r colnames(penguins)`

It contains `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(penguins$flipper_length_mm,na.rm = T)` with NA value in this column been directly removed.

**Create scatter plot:**

The NA in each row is removed through `drop_na` , the resulted fig is saved as png file.

```{r}
penguinsFiltered = drop_na(penguins)
ggplot(data = penguinsFiltered, 
       aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("Bill_FlipperLength.png")
```

## Problem 2

**Create data frame using tibble:**

```{r}
df = tibble(
  randNorm = rnorm(10),
  isPos = randNorm > 0,
  strSeq = c('a1','a2','a3','a4','a5','a6','a7','a8','a9','a10'),
  varFactor = factor(c('a','a','b','b','c','c','c','c','c','c'))
  
)
df
```

**Make mean of each variable:**

```{r, warning=FALSE}
mean(pull(df,randNorm))
mean(pull(df,isPos))
mean(pull(df,strSeq))
mean(pull(df,varFactor))
```

Mean works on the Numeric and Logic type but cannot work on Character and Factor.

```{r, eval = FALSE}
as.numeric(df$isPos)
as.numeric(df$strSeq)
as.numeric(df$varFactor)
```

`as.numeric` turned logic variableto 0 and 1. It turned factor to ordered number series and character to NA. It helps to explain the mean of logic variable.
